A robust framework for variable extrusion width concentric toolpath generation

### 2019-07-11 4_method.tex
rewrite transitioning main section

\subsubsection{Transitioning}
In order to prevent discontinuities in the toolpaths around locations $p$ where $\exists n : R(p) = b^{-1}(n)$ (see \cref{transition_location}), we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
The transition will be placed so as to overlap the locations of $b^{-1}(n)$.

On the one side of the transition we will have $b^*(v_0)=\frac12 n$ and on the other side we will have $b^*(v_1)=\frac12 n + \frac12$.
For all locations on the MAT in between we linearly interpolate the $b^*$ values, so that we can later interpolate the bead widths $W$ linearly as well.

In a narrow wedge region (a.k.a. a cusp) we have to transfer from $n$ to $n+\nicefrac12$ beads; this transition requires a distance.
See \cref{single_bead_strategy_overview}.
The transition will be such that the innermost toolpath makes a \SI{45}{\degree} angle with the medial axis.
The length of the transition along the medial axis depends on the angles involved.
See \cref{transition_length}.
\begin{equation}
t = r_0 (\sin \alpha + \cos \alpha)
\end{equation}

\begin{figure}
\centering
\includegraphics[width=.75\columnwidth]{sources/method/transition_length_v2.pdf}
\caption{Transition length on a line-line segment.}
\label{transition_length}
\end{figure}

The position of a transition should be at a location $p$ where $\exists n : R(p) = b^{-1}(n)$.
However, given the fact that a transition is a region rather than a point, which part of the transition should be ceneterd at $p$?
For a transition from $n$ to $n+\frac12$ beads, we place a fraction of the transition length toward the end with lower $R$ proportional to it's positioning within the region of non-prefered widths:
$ (b^{-1}(n+\frac12) - p(n) ) / (p(n + \frac12) - p(n))$
See \cref{transition_placement}.

\begin{figure}
\centering
\includegraphics[width=.5\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{Transition placement. The anchor position within the transition length is proportional to the transition location within the range between two distances with prefered length. \hl{outdated functions and variables!}}
\label{transition_placement}
\end{figure}

\hl{How to deal with non-marked regions shorter than the transition length?}

The transition needs to be robust against extra fingers in the MAT.
How do we compute the vertex location of an inset on a finger which crosses a transitioning area?
By interpolating the MAT distance between the two ends of the transition, we obtain a stable method for determining the vertex locations of insets.
See \cref{distance_rounding_transition}.
The extra fingers (blue) cause a negligible difference in the inset path (compare the black dashed pat hwith the red dashed path).
\hl{What does it look like for point-line segments or point-point segments?}

>>>>

\subsubsection{Transitioning}
In order to prevent discontinuities in the toolpaths around locations where the bead count changes, we need a way to smoothly transition to a different number of beads around locations where the 3D model has a changing radius.
See \cref{transitions}.
The transition will be placed anchored on each location $v$ where $R(v) = \nicefrac12 b^{-1}(n+1)$ for any lower bead count $n$.
At the start $v_0$ and end $v_1$ of the transition we introduce a new node in the skeleton and connect it to the outline as per the VQ requirement.
We then assign $v_0.B^* = n$ and $v_1.B^* = n + 1$.
If there is any node $v_x$ in between $v_0$ and $v_1$ we assign it a fractional bead count by linear interpolation: $v_x.B^* = n + D(v_0, v_x)/t(n)$, where $D(.)$ is the Euclidean distance measured along the significant bone(s).
See \cref{distance_rounding_transition}.

\begin{figure*}
\centering
\begin{subfigure}{0.9\textwidth}
\includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated__no_transitions.pdf}
\caption{Without transitioning}
\end{subfigure}
\begin{subfigure}{0.9\textwidth}
\includegraphics[width=\columnwidth]{sources/method/wedge_distributed_generated.pdf}
\caption{Transitioning}
\end{subfigure}
\caption{
Discontinuities around regions where the bead count changes are prevented by transition regions (highlighted in cyan).
}
\label{transitions}
\end{figure*}

We determined above that $v_0$ and $v_1$ should be placed around $v$, but their exact position has yet to be specified.
While the Euclidean distance between them is $t(n-1)$, the distance between $v_0$ and the anchor point $v$ is yet to be specified.
We determine the distance between the anchor and the transition start $v_0$ proportial to the positioning of the transition relative to the preferred distances: $D(v_0, v) =  t(n) (b^{-1}(n+1) - p(n) ) / (p(n+1) - p(n))$.
That way the transitions never override the preferred beading.
See \cref{transition_placement}.

\begin{figure}
\centering
\includegraphics[width=.3\columnwidth]{sources/method/transition_location_precise.pdf}
\caption{
Transition placement.
The anchor position within the transition length is proportional to the transition location within the range between two distances with preferred length. 
}
\label{transition_placement}
\end{figure}
